---
title: "Regression discontinuity designs using R"
author: "Sebastian Ellingsen"
date: "9/28/2018"
output:
  ioslides_presentation:
    widescreen: true
    smaller: true
    template: quarterly-report.html

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Introduction

## Applications


## Graphical analysis

## Estimation and inference

## Bandwidth selection



## Example - Incumbency advantage in U.S House elections

## Loading and summarizing data
```{r cars, echo = TRUE}
require(rdrobust)
data(rdrobust_RDsenate)
vote <- rdrobust_RDsenate$vote 
margin <- rdrobust_RDsenate$margin
summary(vote)
summary(margin)


```



## Plot#1:
```{r , echo = TRUE}
rdplot(y = vote, x = margin, title = "RD Plot - Senate Elections Data", x.label = "Vote 
       Share in Election at time t", y.label = "Vote Share in Election at time t+1")
```



## Plot#2:
```{r , echo = TRUE}
rdplot(y = vote, x = margin, binselect = "es", title = "RD Plot - Senate Elections Data",
       x.label = "Vote Share in Election at time t", 
       y.label = "Vote Share in Election at time t+1")
```



## Plot#3:
```{r , echo = TRUE}
rdplot(y = vote, x = margin, binselect = "es", scale = 5, title = "RD Plot - Senate
       Elections Data", x.label = "Vote Share in Election at time t", y.label = "Vote 
       Share in Election at time t+1")
```


## TE stimation and inference
nn

## Estimation#1
```{r , echo = TRUE}
summary(rdrobust(y = vote, x = margin))

```


## Estimation#2
```{r , echo = TRUE}
summary(rdrobust(y = vote, x = margin, all=TRUE))

```



## Bandwidth selection
```{r , echo = TRUE}
summary(rdbwselect(y = vote, x = margin, all = TRUE))
```


## Further examples
- Estimation using uniform kernel: 
```{r e1, echo = TRUE,  results='hide'}
rdrobust(y = vote,x = margin,kernel = "uniform")
```

- Estimation using p = 2 and q = 4: 
```{r , echo = TRUE,  results='hide'}
rdrobust(y = vote,x = margin,p = 2,q = 4)
```

- Estimation using hn = 15 and Ï = hn/bn = 0.8: 
```{r , echo = TRUE,  results='hide'}
rdrobust(y = vote,x = margin,h = 15,rho = 0.8)
```





## References
This application is closely based on the content and exposition in the following publications:

- Calonico, Cattaneo and Titiunik (2015): rdrobust: An R Package for Robust Nonparametric Inference in Regression-Discontinuity Designs, R Journal 7(1): 38-51.
- Cattaneo, Idrobo and Titiunik (2018): A Practical Introduction to Regression Discontinuity Designs: Volume I. Cambridge Elements: Quantitative and Computational Methods for Social Science, Cambridge University Press.
- Cattaneo, Idrobo and Titiunik (2018): A Practical Introduction to Regression Discontinuity Designs: Volume II.
Cambridge Elements: Quantitative and Computational Methods for Social Science, Cambridge University Press.




