---
title: "Regression discontinuity designs using R"
author: "Sebastian Ellingsen"
date: "9/28/2018"
output:
  ioslides_presentation:
    widescreen: true
    smaller: true
    template: quarterly-report.html

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Introduction
In the absence of randomized treatment assignment, some research designs identify the causal effects of non-experimental interventions.

One particularly rigoruous such approach is the regression discontinuity design.

The key feature of the design is that the probability of a treatment changes abruptly at the known threshold.

**Basic idea**: under some assumptions, units with scores barely below the cutoff can be used as counterfactuals for units with scores barely above it.

The regression discontinuity design has been successfully used to study:

- ...
- ...

These slides will cover the basics of this design and how to implement the analysis using R.



## The potential outcomes framework
Each unit has two potential outcomes, $Y_i(1)$ and $Y_i(0)$, corresponding to the outcomes that would be observed under the treatment or control conditions respectively.

$T_i$ is the treatment dummy denoting $1$ if $i$ is assigned to the treatment condition and $0$ otherwise.

Note, we never observe both potential outcomes for any one individual. We observe 

$Y_i~= (1−T_i)\times Y_i(0) +T_i \times Y_i(1).$




## The building blocks

- $n$  units indexed by $i=1,...,n$.

- Each unit has a *running variable*, $X_i$.

- There is a known common cutoff for all the units, $c$.

- Units with $X_i\geq c$ are assigned to the treatment condition, while units with $X_i < c$ are  assigned  to  the  control  condition.

- This  assignment rule is  defined  as $T_i={\bf{1}}(X_i\geq c)$.


**Key feature of the RD design**: probability of treatment is a function of the score and it changes discontinuously at the cutoff.
 
## Application - Incumbency advantage in US House elections


## Graphical analysis

## Estimation and inference

## Bandwidth selection



## Example - Incumbency advantage in U.S House elections

## Loading and summarizing data
```{r cars, echo = TRUE}
require(rdrobust)
data(rdrobust_RDsenate)
vote <- rdrobust_RDsenate$vote 
margin <- rdrobust_RDsenate$margin
summary(vote)
summary(margin)


```



## Plot#1:
```{r , echo = TRUE}
rdplot(y = vote, x = margin, title = "RD Plot - Senate Elections Data", x.label = "Vote 
       Share in Election at time t", y.label = "Vote Share in Election at time t+1")
```



## Plot#2:
```{r , echo = TRUE}
rdplot(y = vote, x = margin, binselect = "es", title = "RD Plot - Senate Elections Data",
       x.label = "Vote Share in Election at time t", 
       y.label = "Vote Share in Election at time t+1")
```



## Plot#3:
```{r , echo = TRUE}
rdplot(y = vote, x = margin, binselect = "es", scale = 5, title = "RD Plot - Senate
       Elections Data", x.label = "Vote Share in Election at time t", y.label = "Vote 
       Share in Election at time t+1")
```


## TE stimation and inference
nn

## Estimation#1
```{r , echo = TRUE}
summary(rdrobust(y = vote, x = margin))

```


## Estimation#2
```{r , echo = TRUE}
summary(rdrobust(y = vote, x = margin, all=TRUE))

```



## Bandwidth selection
```{r , echo = TRUE}
summary(rdbwselect(y = vote, x = margin, all = TRUE))
```


## Further examples
- Estimation using uniform kernel: 
```{r e1, echo = TRUE,  results='hide'}
rdrobust(y = vote,x = margin,kernel = "uniform")
```

- Estimation using p = 2 and q = 4: 
```{r , echo = TRUE,  results='hide'}
rdrobust(y = vote,x = margin,p = 2,q = 4)
```

- Estimation using hn = 15 and ρ = hn/bn = 0.8: 
```{r , echo = TRUE,  results='hide'}
rdrobust(y = vote,x = margin,h = 15,rho = 0.8)
```





## References
This application is closely based on the content and exposition in the following publications:

- Calonico, Cattaneo and Titiunik (2015): rdrobust: An R Package for Robust Nonparametric Inference in Regression-Discontinuity Designs, R Journal 7(1): 38-51.
- Cattaneo, Idrobo and Titiunik (2018): A Practical Introduction to Regression Discontinuity Designs: Volume I. Cambridge Elements: Quantitative and Computational Methods for Social Science, Cambridge University Press.
- Cattaneo, Idrobo and Titiunik (2018): A Practical Introduction to Regression Discontinuity Designs: Volume II.
Cambridge Elements: Quantitative and Computational Methods for Social Science, Cambridge University Press.




